---
title: "**【Visualizing Jazz Musicians】**"
output: 
  html_document:
    toc: true
    toc_float: true
    df_print: paged
---

**$\mathcal{YiHsin}\;\mathcal{Lu}$**

****

### **Recap**

* Genre and record label
* PCA vs t-SNE
* Main plots

### **Current Progress**

* Data matrices: genre, record label
* Active years
* Compare zoom-in plot with


```{r include=FALSE}
library(knitr)
library(dplyr)
library(flextable)
library(magrittr)
library(kableExtra)
library(tidytext)
library(tidyverse)
library(plot.matrix)
library(stringr)
library(micropan)
library(ggpubr)
library(highcharter)
library(ggpubr)
library(tm)
library("SnowballC")
library("wordcloud")
library("RColorBrewer")
library(wordcloud2)
library(viridisLite)
library(Rtsne)
library(qvalue)
library(jaccard)
library(lsa)
library(patchwork)
load("D:/jazz_visual/0831.RData")
```

****

# **1 Data Matrices**

## 1.1 The Data{.tabset}

### 1.1.1 Genres

```{r echo=FALSE,warning=FALSE}
M_genre
```

```{r echo=FALSE,warning=FALSE}
M_genreHP
```

### 1.1.2 Record Labels

```{r echo=FALSE,warning=FALSE}
M_rl.hp
```

****

## 1.2 PCA{.tabset}

### 1.2.1 Genres(34)

```{r echo=FALSE,warning=FALSE}
plot(cor_genre$w[,1],-cor_genre$w[,2],type="n",xlab="W[,1]",ylab="W[,2]",main="Genre",cex.axis=1.2,cex.lab=1.2,cex.main=1.6)
text(cor_genre$w[,1],-cor_genre$w[,2],cor_genre$namew)
abline(h=0,v=0,lwd=1.2)
```


### 1.1.1 Genres(21)

```{r echo=FALSE,warning=FALSE}
plot(cor_genreHP$w[,1],-cor_genreHP$w[,2],type="n",xlab="W[,1]",ylab="W[,2]",main="Genre",cex.axis=1.2,cex.lab=1.2,cex.main=1.6)
text(cor_genreHP$w[,1],-cor_genreHP$w[,2],cor_genreHP$namew,xpd=NA)
abline(h=0,v=0,lwd=1.2)
```


### 1.1.2 Record Labels

```{r echo=FALSE,warning=FALSE}
plot(cor_rl.hp$w[,1],-cor_rl.hp$w[,2],type="n",xlab="W[,1]",ylab="W[,2]",main="Record Label",cex.axis=1.2,cex.lab=1.2,cex.main=1.6)
text(cor_rl.hp$w[,1],-cor_rl.hp$w[,2],cor_rl.hp $namew)
abline(h=0,v=0,lwd=1.2)
```

****

# **2 Active Years**

## {.tabset}

### Collection

```{r echo=FALSE,warning=FALSE}
Mtable_ysa
```

### Matrix

```{r echo=FALSE,warning=FALSE}
M_ysa
```

# **3 Compare with zoom-in plot**

* [Linked jazz](https://linkedjazz.org/network/)
* [music map](https://www.music-map.com/)
* [spotify](https://open.spotify.com/)
* [youtube](https://www.youtube.com/)

## 3.1 Zoom in{.tabset}

### Wynton Marsalis

* [Linked Jazz](https://linkedjazz.org/network/?person=Wynton_Marsalis)
* [Music-Map](https://www.music-map.com/wynton+marsalis)

```{r echo=FALSE,warning=FALSE}
Wynton
```


****

### Roy Hargrove

* [Linked Jazz](https://linkedjazz.org/network/?person=Roy_Hargrove)
* [Music-Map](https://www.music-map.com/roy+hargrove)

```{r echo=FALSE,warning=FALSE}
Roy
```


****

### Miles Davis

* [Linked Jazz](https://linkedjazz.org/network/?person=Miles_Davis)
* [Music-Map](https://www.music-map.com/miles+davis)

```{r echo=FALSE,warning=FALSE}
Miles
```



****

# **4 Remarks**

* No significant clusters in PCA map
* Multi-value classification problem
* Complete the data matrices

