---
title: "**【Data Matrices: Genre, Record Label, Years Active】**"
output: 
  html_document:
    toc: true
    toc_float: true
    df_print: paged
---

**$\mathcal{YiHsin}\;\mathcal{Lu}$**


```{r include=FALSE}
library(knitr)
library(dplyr)
library(flextable)
library(magrittr)
library(kableExtra)
library(tidytext)
library(tidyverse)
library(plot.matrix)
library(stringr)
library(micropan)
library(ggpubr)
library(highcharter)
library(ggpubr)
library(tm)
library("SnowballC")
library("wordcloud")
library("RColorBrewer")
library(wordcloud2)
library(viridisLite)
library(Rtsne)
library(qvalue)
library(jaccard)
load("D:/jazz_visual/0809-1.RData")
```

# **Recap**

* Combination with Jaccard
* t-SNE for the matrices

# **Explanation**

* Jaccard: vector with many "0"
* Other method: vector without any "0"
* Mixed two kind of methods

# **Data Matrices**

* genre
  + drop the "once" data
  + hand-pick
* record label
  + drop the "once" data
* years active
  + year to years
  + t-SNE
  
****  

## **1. Genre**

```{r echo=FALSE}
genre_matrix1
```

****

## **2. Record Label**

```{r echo=FALSE}
RL_matrix1
```

****

## **3. Years Active**

### **3.1 Year**

```{r echo=FALSE}
YA_matrix
```

```{r echo=FALSE}
YA %>% 
  filter(!is.na(year)) %>% 
  count(year) %>% 
  hchart('column', hcaes(x = 'year', y = 'n')) %>% 
  hc_title(text = "YearsActive")
```

****

### **3.2 Years**

```{r echo=FALSE}
YsA_matrix
```

```{r echo=FALSE}
YsA %>% 
  filter(!is.na(year)) %>% 
  count(year) %>% 
  hchart('column', hcaes(x = 'year', y = 'n')) %>% 
  hc_title(text = "YearsActive")
```


****

### **3.3 Visualization**

* data: years
* color: years
```{r echo=FALSE}
hchart(visualTsne_YsA, 'scatter', hcaes(x=tsne1, y=tsne2, group = years))
```
* data: year
* color: year
```{r echo=FALSE}
hchart(visualTsne_YA, 'scatter', hcaes(x=tsne1, y=tsne2, group = year))
```
* data: year
* color: years
```{r echo=FALSE}
hchart(visualTsne_YA, 'scatter', hcaes(x=tsne1, y=tsne2, group = years))
```

****

# **Main Plot**

```{r echo=FALSE}
load("D:/jazz_visual/0808-1.RData")
ggplot(visualTsne_jacInst, aes(x=tsne1, y=tsne2)) +
  geom_point(color = visualTsne_jacInst$hex)
```
