---
title: "**【Jazz Musicians Data Visualization】**"
author: " *Yi-Hsin Lu* "
date: "April 13 2022"
output: html_document
---

```{r include=FALSE}
#packages
library(knitr)
library(dplyr)
library(flextable)
library(magrittr)
library(kableExtra)
library(tidytext)
library(tidyverse)
library(plot.matrix)
library(stringr)
library(micropan)
library(ggpubr)
library(highcharter)
```

****
### **Recap**
* Data collection
* Cleaning

****
### **Text Mining on abstract**

* Abstract 
* Tokens(n_grams)
* One-hot encoding
* Distance matrix
* MDS

****

#### **Abstract**

```{r echo=FALSE}
M_table=read.csv('D:/jazz/Jazz_visual/csv/Musician_table.csv',row.names = 1, header= TRUE)
abstract = read.csv('D:/jazz/Jazz_visual/csv/Mus_abstract.csv')

kbl(abstract[182:192,],align = "l") %>%
  kable_paper() %>%
  kable_classic(full_width = F) %>%
  scroll_box(width = "100%", height = "400px")
```

#### **Tokens**

```{r include=FALSE}
colnames(abstract)=c("name","word")
abstract_1gram = abstract%>%
  unnest_tokens(words,word)
```

**One-gram**
```{r echo=FALSE}
kbl(abstract_1gram,align = "l") %>%
  kable_paper() %>%
  kable_classic(full_width = T) %>%
  scroll_box(width = "100%", height = "400px")%>%
  kable_styling(font_size = 18)
```
token
```{r include=FALSE}
colnames(abstract_1gram)=c("name","word")
data(stop_words)
abstract_1gram = abstract_1gram%>%
  anti_join(stop_words)

tokens = abstract_1gram%>%
  group_by()%>%
  count(word,sort=TRUE)%>%
  ungroup()
```

```{r echo=FALSE}
kable(tokens[1:10,],format = "markdown", digits = 3, align = "l")

```
**Two-grams**

```{r include=FALSE}
abstract_2gram <- abstract %>%
  unnest_tokens(words, word, token = "ngrams", n = 2)

colnames(abstract_2gram)=c("name","word")
data(stop_words)
abstract_2gram = abstract_2gram%>%
  anti_join(stop_words)

tokens_2gram = abstract_2gram%>%
  group_by()%>%
  count(word,sort=TRUE)%>%
  ungroup()
```

```{r echo=FALSE}
kbl(abstract_2gram,align = "l") %>%
  kable_paper() %>%
  kable_classic(full_width = T) %>%
  scroll_box(width = "100%", height = "400px")%>%
  kable_styling(font_size = 18)
```

```{r echo=FALSE}
kable(tokens_2gram[1:10,],format = "markdown", digits = 3, align = "l")

```

### **One-Hot Encoding**

```{r include=FALSE}
musicians = rownames(M_table)

lappend <- function (lst, ...){
lst <- c(lst, list(...))
  return(lst)
}
```

```{r include=FALSE}
token_list = list()

for(mu_n in musicians){
  token_pr = rbind(subset(abstract_1gram,name==mu_n)[2], subset(abstract_2gram,name==mu_n)[2])
  token_list = lappend(token_list, token_pr)
  token_pr = c()
}

```

```{r include=FALSE}
token_sel_1 = read.csv('D:/jazz/Jazz_visual/csv/tokens_1gram.csv', header = TRUE)[1]
token_sel_1 = token_sel_1$word
token_matrix_1 = as.data.frame(matrix(data = 0, nrow = length(musicians), ncol = length(token_sel_1)))
rownames(token_matrix_1) = musicians
colnames(token_matrix_1) = token_sel_1
```

```{r include=FALSE}
token_in = read.csv('D:/jazz/Jazz_visual/csv/instrument.csv', header = TRUE)[1]
colnames(token_in)='word'
token_in = token_in$word
token_matrix_in = as.data.frame(matrix(data = 0, nrow = length(musicians), ncol = length(token_in)))
rownames(token_matrix_in) = musicians
colnames(token_matrix_in) = token_in

#token
for(tokens_i in token_in){
  for(mu_i in 1:length(musicians)){
    if(grepl(tokens_i, token_list[[mu_i]])==TRUE){
      token_matrix_in[mu_i, tokens_i]=1
    }
  }
}
```

```{r}
write.csv(token_matrix_in,"D:/jazz/jazz_visual/csv/token_matrix_in.csv")
```


```{r include=FALSE}
token_sel = rbind(read.csv('D:/jazz/Jazz_visual/csv/tokens_1gram.csv', header = TRUE)[1],read.csv('D:/jazz/Jazz_visual/csv/token_2gram.csv', header = TRUE)[1])
token_sel = token_sel$word
token_matrix = as.data.frame(matrix(data = 0, nrow = length(musicians), ncol = length(token_sel)))
rownames(token_matrix) = musicians
colnames(token_matrix) = token_sel
```

```{r include=FALSE}
for(tokens_i in token_sel){
  for(mu_i in 1:length(musicians)){
    if(grepl(tokens_i, token_list[[mu_i]])==TRUE){
      token_matrix[mu_i, tokens_i]=1
    }
  }
}
```


```{r include=FALSE}
for(tokens_i in token_sel_1){
  for(mu_i in 1:length(musicians)){
    if(grepl(tokens_i, token_list[[mu_i]])==TRUE){
      token_matrix_1[mu_i, tokens_i]=1
    }
  }
}
```

```{r echo=FALSE}
kbl(token_matrix,align = "c") %>%
  kable_paper() %>%
  kable_classic(full_width = F) %>%
  scroll_box(width = "100%", height = "600px")
```

#### **MDS(by jaccard distance matrix)**

```{r include=FALSE}
library(micropan)
mus_dist_jac_1 = distJaccard(token_matrix_1)
mds_musicians_1 <- mus_dist_jac_1 %>%      
  cmdscale() %>%
  as_tibble()
colnames(mds_musicians_1) <- c("Dim.1", "Dim.2")
```

```{r echo=FALSE}
hchart(mds_musicians_1, "scatter", hcaes(x = Dim.1, y = Dim.2, group = musicians))
```

```{r include=FALSE}
library(micropan)
mus_dist_jac = distJaccard(token_matrix)
mds_musicians <- mus_dist_jac %>%      
  cmdscale() %>%
  as_tibble()
colnames(mds_musicians) <- c("Dim.1", "Dim.2")
```

```{r echo=FALSE}
library(highcharter)
hchart(mds_musicians, "scatter", hcaes(x = Dim.1, y = Dim.2, group = musicians))
```

**Color by Instrument**

```{r include=FALSE}
instrument = read.csv('D:/jazz/instrument.csv', header = TRUE)$word

instrument_matrix = as.data.frame(matrix(data = "others", nrow = length(musicians), ncol = 1))
rownames(instrument_matrix) = musicians
colnames(instrument_matrix) = "instrument"
for(inst_i in instrument){
  for(mu_i in 1:length(musicians)){
    if(grepl(inst_i, token_list[[mu_i]])==TRUE){
      instrument_matrix[mu_i, 1]=inst_i
    }
  }
}

```


```{r echo=FALSE}
mds_musicians = cbind(mds_musicians, instrument_matrix)
hchart(mds_musicians, "scatter", hcaes(x = Dim.1, y = Dim.2, group = instrument))
```

****

### **Remark**

* Text mining 
  + tokens
  + n-grams

* Prelim MDS


****

### **What's Next?**
* Visualization
  + t-SNE
  + st-SNE(supervised t-SNE)
  + UMAP
* plot by different "Y" information


****