---
title: "**【Visualizing Jazz Musicians】**"
output: 
  html_document:
    toc: true
    toc_float: true
    df_print: paged
---

**$\mathcal{YiHsin}\;\mathcal{Lu}$**

****

## **Recap**

  * explain combination of jaccard
  * plot color by instrument

```{r include=FALSE}
library(knitr)
library(dplyr)
library(flextable)
library(magrittr)
library(kableExtra)
library(tidytext)
library(tidyverse)
library(plot.matrix)
library(stringr)
library(micropan)
library(ggpubr)
library(highcharter)
library(ggpubr)
library(tm)
library("SnowballC")
library("wordcloud")
library("RColorBrewer")
library(wordcloud2)
library(viridisLite)
library(Rtsne)
library(qvalue)
library(jaccard)
library(lsa)
library(patchwork)
load("D:/jazz_visual/0818.RData")
```

# **1. Data Matrices**

****

## 1.1 Genres

```{r echo=FALSE}
plot(cor_genre$w[,1],-cor_genre$w[,2],type="n",xlab="W[,1]",ylab="W[,2]",main="Genre",cex.axis=1.2,cex.lab=1.2,cex.main=1.6)
text(cor_genre$w[,1],-cor_genre$w[,2],cor_genre$namew)
abline(h=0,v=0,lwd=1.2)
```

****

## 1.2 Record Label

```{r echo=FALSE}
plot(cor_rl$w[,1],-cor_rl$w[,2],type="n",xlab="W[,1]",ylab="W[,2]",main="Record Label",cex.axis=1.2,cex.lab=1.2,cex.main=1.6)
text(cor_rl$w[,1],-cor_rl$w[,2],cor_rl$namew)
abline(h=0,v=0,lwd=1.2)
```

****

# **2. Visualization**

```{r echo=FALSE}
visualpca_plot+visualTsne_plot
```

****

# **3. Main Plots**

****

## 3.1 Entire combination

* $\mathcal{X}_i$: affinity matrix for each information
* for $i$:
  + instrument
  + yearsActive
  + genre
  + recordLabel
* $\large{\mathcal{X}_{entire} =\sqrt{\mathcal{X}_{instrument}^2+\mathcal{X}_{yearsActive}^2+\mathcal{X}_{genre}^2+\mathcal{X}_{recordLabel}^2}}$

```{r echo=FALSE}
ggplot(visualTsne_ComAll, aes(x=tsne1, y=tsne2, label=name))+
  geom_point() +geom_text(hjust=0, vjust=0)

hchart(visualTsne_ComAll, 'scatter', hcaes(x=tsne1, y=tsne2, group=name))
```

****

## 3.2 Zoom in{.tabset}

### 3.2.1 Wynton Marsalis

```{r echo=FALSE,warning=FALSE}
Wynton
```

****

### 3.2.2 Roy Hargrove

```{r echo=FALSE,warning=FALSE}
Roy
```

****

### 3.2.3 Miles Davis

```{r echo=FALSE,warning=FALSE}
Miles
```


****

## 3.3 Weight{.tabset}

### 3.3.1 Instrument

* $\large{\mathcal{X}_{entire} =\sqrt{7\cdot\mathcal{X}_{instrument}^2+\mathcal{X}_{yearsActive}^2+\mathcal{X}_{genre}^2+\mathcal{X}_{recordLabel}^2}}$

```{r echo=FALSE}
ggplot(visualTsne_ComAll.inst, aes(x=tsne1, y=tsne2))+
  geom_point(color = visualTsne_ComAll.inst$hex)
```

****

### 3.3.2 Years Active

* $\large{\mathcal{X}_{entire} =\sqrt{\mathcal{X}_{instrument}^2+7\cdot\mathcal{X}_{yearsActive}^2+\mathcal{X}_{genre}^2+\mathcal{X}_{recordLabel}^2}}$

```{r echo=FALSE}
ggplot(visualTsne_ComAll.ysa, aes(x=tsne1, y=tsne2, colour = ysa$year))+
  geom_point()
```
