---
title: "**【Visualizing for Jazz Musicians】**"
output: 
  html_document:
    toc: true
    toc_float: true
    df_print: paged
---

**$\mathcal{YiHsin}\;\mathcal{Lu}$**

****

  
```{r include=FALSE}
library(imputeTS)
library(knitr)
library(dplyr)
library(flextable)
library(magrittr)
library(kableExtra)
library(tidytext)
library(tidyverse)
library(plot.matrix)
library(stringr)
library(ggpubr)
library(highcharter)
library(ggpubr)
library(tm)
library(SnowballC)
library(wordcloud)
library(RColorBrewer)
library(wordcloud2)
library(viridisLite)
library(Rtsne)
library(qvalue)
library(jaccard)
library(lsa)
library(patchwork)
load("D:/jazz_visual/1002.RData")
```


# **1 Active Years**

* middle
* length
* mixture
* color

## **1.1 Data**{.tabset}

### Years

```{r echo=FALSE}
Mtable_ysa.i
```

### Length

```{r echo=FALSE}
hist(len_years$n, breaks = 13, main = "Length")
```

```{r echo=FALSE}
len_years
```

### Length (one-hot encoding)

```{r echo=FALSE}
M_lenyears
```

### Start and the End

```{r echo=FALSE}
Mtable_ya
```

### Middle

```{r echo=FALSE}
hist(Mtable_yamidna$middle, breaks = 20, main = "Middle")
```

```{r echo=FALSE}
Mtable_yamidna
```

### Middle (one-hot encoding)

```{r echo=FALSE}
M_yamid
```

## **1.2 Visualization**{.tabset}

### Middle+Length (Middle)

```{r echo=FALSE}
vis_pca2mid+vis_tsne2mid
```

### Middle+Length (Length)

```{r echo=FALSE}
vis_pca2len+vis_tsne2len
```

### Middle+Length+Years (Middle)

```{r echo=FALSE}
vis_pca3mid+vis_tsne3mid
```

### Middle+Length+Years (Length)

```{r echo=FALSE}
vis_pca3len+vis_tsne3len
```

# **2 Discussion**

* combined information
* power transformation
* LDA alternative Jaccard