---
title: "**【Visualizing for Jazz Musicians】**"
output: 
  html_document:
    toc: true
    toc_float: true
    df_print: paged
---

**$\mathcal{YiHsin}\;\mathcal{Lu}$**

****

## **Recap**

  * Complete the data matrices of active years, genre and record label
  
```{r include=FALSE}
library(knitr)
library(dplyr)
library(flextable)
library(magrittr)
library(kableExtra)
library(tidytext)
library(tidyverse)
library(plot.matrix)
library(stringr)
library(micropan)
library(ggpubr)
library(highcharter)
library(ggpubr)
library(tm)
library("SnowballC")
library("wordcloud")
library("RColorBrewer")
library(wordcloud2)
library(viridisLite)
library(Rtsne)
library(qvalue)
library(jaccard)
library(lsa)
library(patchwork)
load("D:/jazz_visual/0913.RData")
```

****

# **1. All**

```{r echo=FALSE}
ggplot(visualTsne_all, aes(x=tsne1, y=tsne2, label=name))+
  geom_point() +geom_text(hjust=0, vjust=0)

hchart(visualTsne_all, 'scatter', hcaes(x=tsne1, y=tsne2, group=name))
```

****

# 2. **Instruments**

```{r echo=FALSE}
visualpca_plot.inst+visualTsne_plot.inst
```

****

# 2. **Genres**{.tabset}

## Visualization

```{r echo=FALSE}
visualpca_plot.genre+visualTsne_plot.genre
```

****

## PCA for information

* Jaccard before PCA
* the 3 classes

```{r echo=FALSE}
plot(PCA_genreHP$rotation[,1],PCA_genreHP$rotation[,2],type="n",xlab="PC1",ylab="PC2",main="Jazz Genres",cex.axis=1.2,cex.lab=1.2,cex.main=1.6)
text(PCA_genreHP$rotation[,1],PCA_genreHP$rotation[,2],genresHP)
abline(h=0,v=0,lwd=1.2)
```

****

# 2. **Active Years**{.tabset}

## Visualization

```{r echo=FALSE}
visualpca_plot.ysa+visualTsne_plot.ysa
```

****

## PCA for information

* Jaccard before PCA
* the 3 time intervals

```{r echo=FALSE}
plot(PCA_yearsActive$rotation[,1],PCA_yearsActive$rotation[,2],type="n",xlab="PC1",ylab="PC2",main="Active years interval ",cex.axis=1.2,cex.lab=1.2,cex.main=1.6)
text(PCA_yearsActive$rotation[,1],PCA_yearsActive$rotation[,2],years)
abline(h=0,v=0,lwd=1.2)
```

****

# **3. Remark and Discussion**

* Cluster for genres and active years
* Color on active years
* Singal-value and Multi-value