---
title: "**【Visualizing Jazz Musicians】**"
date: 'July 01, 2022'
output: 
  html_document:
    df_print: paged
---

```{r include=FALSE}
library(knitr)
library(dplyr)
library(flextable)
library(magrittr)
library(kableExtra)
library(tidytext)
library(tidyverse)
library(plot.matrix)
library(stringr)
library(micropan)
library(ggpubr)
library(highcharter)
library(ggpubr)
library(tm)
library(SnowballC)
library(wordcloud)
library(RColorBrewer)
library(wordcloud2)
load("D:/jazz/Jazz_visual/0701.RData")
```

****

### **Recap**
3 classes in instrument

* Beats
  + drummer
  + bassist
  + percussionist
  + keyboardist
* Wind
  + pianist
  + composer
  + saxophonist
  + flute
  + trumpeter
  + trombonist
  + horn
* vocal
  + vocalist
  + singer
  + songwriter
  + guitarist
  + producer

****

```{r echo=FALSE}
Mtable_instclass
```

****

### **MDS**

* tokens matrix
* affinity matrix(by Jaccard)
* MDS
* color by first instrument

****

```{r echo=FALSE}
hchart(mds_1stinst, "scatter", hcaes(x = D1, y = D2, group = instrument))
```

****

### **MDS (3 classes)**

```{r echo=FALSE}
hchart(mds_1stinst, "scatter", hcaes(x = D1, y = D2, group = class))
```

****

### **Next**

* LDA, t-SNE
* multi-value classification
* color by genre and yearActive